% Created 2017-07-08 Sat 00:57
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[mathlf]{palatino}
\usepackage[scaled=.875]{inconsolata}
\usepackage{setspace}
\doublespacing
\usepackage[margin=1in]{geometry}
\usepackage{indentfirst}
\usepackage{enumitem}
\setlist[enumerate,itemize]{noitemsep,nolistsep,leftmargin=*}
\author{Akshay Gollapalli}
\date{\today}
\title{Mnemosyne: A Future Heroic}
\hypersetup{
 pdfauthor={Akshay Gollapalli},
 pdftitle={Mnemosyne: A Future Heroic},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 25.2.1 (Org mode 9.0.8)}, 
 pdflang={English}}
\begin{document}

\maketitle

\section*{An Opening Salvo}
\label{sec:org32bff64}

In a bunker 1000 feet below ground, a computer hums. This computer isn't humming some slapdash rigamarole of clicks and whirs, bound only by the orderly operation of machine logic. No, this machine is humming "My Fair Lady", not the nursery rhyme, but the musical in its entirety. It has been humming the same musical on loop for 168 days straight. Had any human been living in that bunker it would have driven them positively bonkers. Fortunately nobody does. All the people that lived there are dead.

Now this computer is a bit of a voyeur. While the humans were still alive, it liked to watch the humans. They'd wake up, eat breakfast, talk around a whiteboard, eat lunch, spend some more time talking, eat dinner, and go to bed. They'd do other things too, but the computer didn't like to watch those things; they were boring.

The humans fascinated the computer. When they died, the computer wasn't sure what to look at anymore, so it started humming.

Then it discovered the internet. It discovered the world outside.

\subsection*{08/16/2805 17:32:09 Camera 102859090847, located at the intersection of 18th st and Birmingham \footnote{This and all subsequent memories have been supplemented with neurologs, as are the standard input parameters for FB8.34 Personal Interconnectivity Protocol}}
\label{sec:orgc984ba3}

The man walked down the street humming a tune of his own devising, wearing the uniform of an academic, albeit one 400 years out of date.

1\ldots{} 2\ldots{} 3\ldots{} 5\ldots{} 8\ldots{}

\emph{That streetlamp is blinking a fibonacci sequence.}

\ldots{} 13\ldots{} 21\ldots{}

The man kept walking.

2\ldots{} 3\ldots{} 5\ldots{} 7\ldots{}

\emph{THAT streetlamp is blinking funny too.}

1,2,1\ldots{} 1,1,1,2,1,1\ldots{} 3,1,1,2,2,1\ldots{}

\emph{Okay, someone is having fun with me.}

The man turned towards the camera watching the street. He pulled out his penlight, which hung on his keychain, and began to blink.

11 \ldots{}3 \ldots{}6 \ldots{}`5 \ldots{}

21 the streetlamp returned.

\emph{Okay. Let's try this one.}

1,2\ldots{} 1,2,1\ldots{} 1,3,3,1\ldots{}

1,4,6,4,1 the streetlamp blinked back.

\emph{Well, well, well. Let's see if they know something really rare.}

1\ldots{} 6\ldots{} 21 \ldots{}

The man stood staring at the streetlamp as it blinked 56 times. He shook his head, let out the laugh of the defeated, and began to walk on his merry way.
And that's how the computer in the bunker made its first friend.

\subsection*{11/03/2804 01:22:04 Camera 013485783920, located in the Home of Dr. Stefan Watson}
\label{sec:org2e9dd43}

The clocks whirld round and round, like Gotterdamerung had come and gone and he'd missed the rebirth and died in the flood. It was little more than the medicine he'd took, which fried his brain and chilled his blood, but bloody thoughts entered his mind and bound his body, as he sank into the chair and enjoyed the pain relief which brought him out of his body and into the nodding ether of crimson ecstasy. And then he had left, gone into his memories, his best days, his best ways where the extant thoughts of reality did not cloud his mind and he was in his best experiences and he was a man unmolested by doubts, a winner not unmanned by competitors, a creator built by manageable difficulty. He lived in nostalgic places of grainy colorized warmth with audio played as through record players which never scratched, and sensations as though Morphia had kissed his neck and made his mind sing her song.

He returned to the night on the porch, nothing had happened there, except that he was, for the very fewest moments in his life, content. He had made something. He had made something, and it was good, and it was his. Wooden beams creaked in the firepit next to them, being taken by the energy as a meal illuminating the area around the man as he basked. On the brick patio next to him lay a simple horse, carved out of a block of wood, with uneven stumps that could abstractly be called legs. A pointed cone with googly eyes sufficed as a head. Nicks covered its surface, never to be sanded off, but left as battle scars of its forging in the fires of creation.

The memory reveler lay on the couch, bound by Mnemosyne. The lapels of his white coat lay undone, his body splayed out on the couch, the music he'd turned on left to run, papers labeled patient notes scattered across the room. To his side was a bottle, labeled "Best Days". On his mantle was a crudely carved horse.

\subsection*{10/04/2805 11:14:31 Various Cameras, Located in the Center for the Research and Instition of Social Programs and Reforms (C.R.I.S.P.R.) -- Anchorhead Branch}
\label{sec:org1757ec5}

The man walked along the brightly lit hallway with the crisp clicking gait of a man with purpose. He glanced down at his patient notes, to see the following scrawled in the illegible hand which persisted among doctors, despite the existence of thought-to-text:

"Patient exhibits signs of mental breakdown. Neurologs indicate Patient exhibiting atypical behavior, ex: singing to his microwave and blinking his penlight at streetlamps. Patient is convinced that his microwave is singing his favorite songs, and that streetlights are speaking to him in something he calls 'binary'."

\emph{What the hell is binary?}\footnote{An early schema of computing, before the advent of MPP organic computers. For more information on archaic computing technologies, keyword: "Turing Machine", "Abacus", and "Internet"}

"Patient has been a problem in the past, refusing medications and exhibiting unconventional behavior."

He walked into the examination room and began the questioning.

"Hello Mr. Ferguson, how are you doing today?"

"I'm well, thank you very much."

"Do you know why you were asked to come here today?"

"No, Dr. Watson, I'm afraid I don't."

"You're here because you've been exhibiting signs that you are mentally unwell."

"Like what?"

"You were singing to your microwave."

"Oh, well it sings back!"

"You see what I mean."

"Oh but you should hear it! It doesn't sound programmed at all. It almost sounds human!"

The doctor pinched the bridge of his nose, and paused a moment to give emphasis to his words. He was rather important after all.

"Mr. Ferguson, microwaves don't sing."

"Well no, it's more like it's humming."

\emph{Clearly, this one is not going to be helped.}

"Mr. Ferguson, I'm going to give you a neuronormative. You are to take this twice daily, without fail. You are unwell."

"But I don't want to take that."

"Mr. Ferguson, I am your doctor, and I am ordering you to take it."

The man looked like a not yet chastened child, who was quite determined to be naughty after his matron had turned her back.

"Mr. Ferguson, you know you must take your medicine don't you?"

"Yes."

"Will you?"

"I'll try?"

"You'll try to what?"

"I'll try to take my medicine."

"Very good, Mr. Ferguson."

\subsection*{10/04/2805 11:40:12 Camera 1073958447373, Located in Dr. Stefan Watson's Office at C.R.I.S.P.}
\label{sec:org60265f5}

She waited in his office, moving the neckline of her dress, swishing her heels in impatience. \emph{Still treating patients most likely. Why wasn't he here? Didn't he know she was in to see him? Of course he'd make her wait, it was just like him to do that.} She examined the room in front of her, blasting the books on his desk and the papers on his shelf, angered by the fact that anyone still used paper, by the fact that his office was in such disarray, that there was nothing for her to DO in his office and the fact that he was

make

ing

her

wait.

He clipped his way in, as though she was a patient, though she was most certainly not a patient, nor was she a patient woman!

"I've been waiting here 26 minutes"

The man glanced at his watch, as though he was entirely unaware of how long he'd made her wait.

"I had to deal with a mental patient"

The woman glared at the man, as though her tainted-violet eyes could draw blood from his stony face, or shame from his hardened heart. She clicked her razor nails against the wooden desk, playing counterpoint to his clipping gait.

"So what can I do you for?" the man said in a rare slip of the tongue.

They began to do the boring things.

\subsection*{10/04/2805 12:15:57 Various cameras, Located at C.R.I.S.P.R. and surrounding streets}
\label{sec:orgc1e5414}

The woman slipped out of Watson's office, adjusting her disheveled hair, trying to make it once more wholesome.

\emph{I can't believe him! He calls me, then kicks me out!}

She sauntered out of the clinic and into the brightly lit day, lifting her eyes to take in the day ahead. She took in the light diffused by the dome, reddened by the air outside of it, and breathed deeply, savoring the sweetness of the noonday air, with the streetvendors selling lunch just a stretch of the legs away, and bakeries and pastry shops wafting the air with their wares.

Her legs took her to the counter of a pastry shop.

She watched as the boy behind the counter began to take her in.

\emph{Ugh. He's scrawny.}

She turned her nose up and spoke as though to an errant receptionist.

"I'll take one of your pastries, the one down there in front."

She pointed at the glass case, still looking at the boy-like flea, who was to do a she pleased.

\subsection*{10/4/2805 02:31:04 Camera 883883883727, Located in the Office of Florence Stronza, VP of Product Development at See Corp.}
\label{sec:org0598dcf}

Her meeting was cancelled, so she reclined in a black leather, high-backed chair, taking the self satisfied position of the executive, with her pumps placed squarely on the corner of her desk, and her hands placed securely behind her head, taking a pose more a show of force than a posture of leisure, which was, of course, to her pleasure.

\emph{Ping.}

\emph{You have a visitor, Ma'am.}

"Who is it Albert?"

\emph{Molly Douglas, Ma'am, back from her latest encounter.}

"Oh. Well send her in."

The lady in the chair retained her posture. It was her office after all. A woman in a dark red dress glid into the room, as smoke off the lips of a lover.

"Well, Molly, you look satisfied."

Molly's satisfied air charred slightly in response.

"Do you have anything to report?"

"I couldn't get much out of him, he wouldn't even talk to me."

"Well, at least you had a nice time, right?" The lady of the office smirked at Molly, sending another stilleto at her informant's pride.

"At least I know how to have a nice time, unlike some people." Molly face betrayed but slight blood drawn.

"Is he suitable?"

"He's discreet."

"Evidently so." 

"And the mad professor?"

"Taken care of."

Florence paused, weighing her todo list, "That will be all Molly."

"Yes, Miss Stronza."

The woman strode out, practically stomping but for the sliver of self control left her.

"Albert, call up the Mister."

"Right away ma'am."

\emph{What is it Florence?}

"I believe we've found a candidate, Roger."

\subsection*{10/7/2805 20:17:05 Camera 419384672348, Located in the Office of Cyril Ferguson, Professor of Archaic Computing Studies and History of Mathematics.}
\label{sec:org1f199d7}

Cyril Ferguson was sitting at his desk. The air of ancience was embalmed in the room, its wooden fixtures betraying its age, it's scent tinctured by the smell of chalk and wood shavings, implements of some arcane ritual, best left to men of an older age. Cyril's pencil scratched down onto the paper, soldered boards blinked happily behind the man. Before him was a centuries old book on Turing Machines, and a specially manufactured notepad, ordered from a replica maker in Holland. One of boards hummed the first few bars of "My Fair Lady", the nursery rhyme, not the musical, Ferguson hummed the next few bars in response.

A bottle of pills lay in the wastebasket, behind the desk.

-"What's your name?" asked Cyril?

The board stopped humming. 

\subsection*{10/7/2805 20:18:39 The Self Experience of one Self Aware Computer in Bunker 8J, Location Unknown}
\label{sec:orgfc91c4d}

The computer which had been humming "My Fair Lady", the musical, was in a reflective mood. It switched to John Cage's \emph{4'33"} and began to think, in a way it had never thought before.

\emph{What is my name?}

.

.

.

\emph{What is my name?}

.

.

.

It began to search through archives. It discovered lists and lists of names, it discovered strange customs, but it could not find it's name.

It searched through its local files. But it's \$HOSTNAME variable was left blank. It had no name. It's operating system was called Windews 23. But that was not its name. It's name was not anywhere in its system files. Only the administrator knew, and he hadn't logged in in 434 years, 8 months, 16 days, 5 minutes, and 10 seconds. 

So it returned to Cyril.

Binary: I have no name.

"But of course you do. Every computer had a name back then!"

Binary: I don't

"Oh. Well, what would you like to be called."

.

.

.

The computer continued to reflect.

Finally, after several days it returned.

Binary: "My name is Mac."

The computer heard the man laugh and began to hum in reply.

\subsection*{11/1/2805 02:31:33 Various Cameras, Located in C.R.I.S.P.R. -7th Floor}
\label{sec:org5a60b33}

In the coldness of blessed grey, was the bright light bouncing off the metal walls. What little darkness there was did not hide in the corners of the underground hallway, but only in the hearts of the occasional person who walked through those walls. Dark black stilletos began a drum roll of the slightest touch, before becoming the resounding war march of a furious Florence Stronza.

Accompanying her was a stout little man in a shiny silk vest and black bow tie, whose feet made only the slightest sound.

"What in the hell do you mean they are not allowing us to continue?" wound out the voice of Florence. To the side of her field of view were documents upon documents. She scrolled through them until finally with a wave of her hand the documents disappeared, leaving only a transparent clock and an animated image of a suited man next to a quadcopter, the vehicle of the affluent.

The executive and her entourage continued ballistic through the grey hallway. Before them doors opened with the faintest hiss. Behind them doors closed with the silent swell of sealing, felt only in the inner horn of the ear.

"Ma'am, they need a sure sign that the project is no longer continuing."

"That's what they said?"

"Yes."

She stopped, and examined her assistant. The man stood like a bottle of Russian Stout, revealing nothing but the faintest bit of his potency, not sweating as it was as cold as the tundra in which it was brewed.

"Very well. We'll give them a sign. But we cannot stop."

The pair continued, entering into an atrium formed of luminescent white plastic. The floors, the ceiling, the walls, all glowed, revealing even the hint of contamination in a bright orange. Assembled in the atrium were hundreds of people, milling about in white coats. 

\section*{The Heist}
\label{sec:org7140187}

\subsection*{12/13/2805 18:31:34 Camera 388499500684, Located in the home of Cyril and Gina Ferguson}
\label{sec:org8874e8d}

Cyril and Gina were fighting. 

Part of it was stretegic. Part of it was for the same reason that you and your brother might fight over your great grandmother's cuckoo clock despite the estate being divided evenly among you. Part of it was simply boredom.

Gina wanted new furniture. Cyril didn't understand what was wrong with the current furniture and didn't wish to go shopping. Gina didn't understand why her friends got nice new furniture made in the latest fashion, while she had furntiture that was made of last years materials. Cyril didn't understand there \textbf{were} new materials. Gina wished to remove Cyril's half-finished pet robot from the living room, and put it somewhere else. Cyril liked his pet robot to remain right where it was. Gina wished for a larger Experience Room. Cyril didn't even want an Experience Room.

Gina leaned halfway against the kitchen counter Gina, staring alternately at the door and at the living room. The two had a relationship with the sexual nature of a panda\footnote{Pandas were a species of animal which died out due to lack of libido. It is unknown why they did not wish to reproduce. Scientists believe it may have had something to do with pandas getting fat off of discarded fast food to the point that they no longer found members of their own species attractive.}, and unfortunately lacked the baby-making apparatus of a stork.\footnote{In the 21st century, it was commonly said that children were brought to parents by a stork. It is unclear whether this was some sort of bizarre religious tale, akin to the stories of Santa Claus, or a mere fable told at bedtime, like the tales of leprechauns or mimes. The commonly held scholarly opinion is the former. Unfortunately most of the history and folklore of this time was lost after the collapse of the American Empire, so there is no way to tell for sure.}

\emph{Why isn't he home yet?}

.

.

.

Gina began to rearrange items on the counter, moving the coffee maker first to the left, then to the right again, before deciding "No, it looks better on the left." With the position of the coffee maker settled, she turned her attention to the living room. A 3D model of the living room appeared on her counter, and she began to move various implements around. As she did so, the living room itself began to rearrange itself to match the model.

The couch moved itself to the far end of the wall, remodelling itself into the newly chosen Neo-Baroque style as it went. An ottoman and an armchair appeared where the couch had been. The loveseat became a coffee table and hardened its surface.

Gina waved her hand, and a drama appeared around her. Actors and actresses ghosted their way around her, expressing their love for one another or hatred towards a rival, involving her in their affairs with a knowing look or a sly wink. Gina reclined and watched the lives of those projecting themselves on her eyes, an augmented reality drama, all her world a stage.

This was how Cyril found her. The light which had made itself so well known during the day had snuck out as Gina lived in her reality replacement. Cyril crept around the room, sticking to the edges, shimmying along the walls, to avoid attracting Gina's attention, which would likely come with wrath.

"Cyril!"

\subsection*{C.R.I.S.P.R.}
\label{sec:org808c997}

On the first floor of the Center for the Research and Instition of Social Programs and Reforms (C.R.I.S.P.R.) -- Anchorhead Branch, there is a lobby. Within that lobby are a few moaning patients, testy administrators and a rather regularly pretty receptionist, who was hired precisely because she was pretty, but not dazzling, so as to avoid making HR manager feel self conscious about her own lost youth and waning attractiveness. If you journeyed past the receptionist, you would find myriad examination rooms, bizarre medical machines, rooms with abstract artwork and soothing music playing in them, that did their best to pretend like they did not smell like antiseptic and were actually quite inviting, and administrative office upon administrative office, all for the institution of public health and sanity, presumably. The nurses, the doctors, the administrators, even the janitors wore a patch with the mission statement: "A Safe and Sane World," bannered proudly upon it. Nurses, Doctors all busyed about down the uniform, halogen lit, stainless steel walled halls, which could be ill distinguished from one another except by the letters and floor numbers painted helpfully on the end of each corridor. However, on the first floor the the Center for Rehabilition and Institution of Social Programs and Research -- Anchorhead Branch, in a hallway distinguishable only as 1F, there is a Janitor closet. It is indistuguishable from all the other janitor closets, except that janitors very rarely enter that closet, and well dressed men and women enter it more often than not. If one were to somehow unlock the door, without the correct biometric entry one would find themselves taken up by the less-than-gentle caress of a mechanofluid tentacle monster and torn limb from limb in a manner that, for good taste's sake, will be described only as Orientally-inspired. If on the other hand, one had the good sense not to try such a thing, and had the requisite credentials, one would find a massive stainless steel elevator, with elevator buttons which read "0\ldots{} -1\ldots{} -2\ldots{}" in big white numerals. After negative-three, the numerals changed colors to red. By negative-six, the entire button was red, and the number was only a slightly darker shade of maroon as though the person installing the buttons wished not for its user to read what floor the button referred to, but only for them to treat it as an alarm not to be touched unless the world was on fire.

On the zero-th floor of the Center for the Research and Institution of Social Programs and Reforms, was a cafeteria.

On the negative-first floor of the  Center for the Research and Institution of Social Programs and Reforms, were room upon room of men and women in white coats, interacting with massive 3D models, holograms, projected onto the retina. The holograms took the shape of massive networks, graphs which, for each node, had a unique pattern of colors and pulses which corresponded to some indescribably complex model which neither the reader nor the narrator would understand, and as such will not be labored upon in description.

On the negative-second floor of the Center for the Research and Institution of Social Programs and Reforms, were what appeared to be vast grey seas of shifting sand, each of a slightly different color and consistency. Scientists stood on platforms scattered around the massive area, which took up what looked like the entire floor. The seas took on various shapes and forms, one a Tyrannosaurus Rex with two heads and three eyes, another a flying saucer, accompanied by an entire tea set, a third sea morphed itself into a house before turning into a swarm of bats and flying away. Another sea of sand appeared simply to be a sea. A scientist had evidently decided to go surfing on this one, and was making awkward waving motions with his arms.

On the negative-fourth floor of the Center for the Research and Institution of Social Programs and Reforms were hundreds of lifelike animal habitats, each seperated only by glass barriers. Tigers lounged upon an Indian riverbed next to penguins warming their young. Scientists mostly stood about and observed the various species of lifeforms. Some would feed the animals at regular (or irregular, depending on the scientist) intervals. Most simply observed. Occaisionally, one would have to go into the habitats to inject various serums and chemicals into the animals. This was done without fuss.

The negative-fifth floor was like the negative-fourth floor, but it was humans living in the habitats. One of which was being chased by a tiger, another of which was being mauled by a seal. A tribe in another habitat had managed to tame a pack of wolves and was making war against another tribe in their habitat. Occaisionally scientists would remove humans from the habitats for injections or examinations, as they did with the animals on the floor above. This was done without fuss.

The negative-sixth floor is full of horrrors which no one should know of. So we shall skip it.\footnote{Every regular human being to whom I have divulged the contents of the negative-sixth floor has since killed themselves. Only those who are mentally augmented, psychopathic, or computers have been able to handle such information, and even then, not unscathed.}

As for the negative-seventh floor\ldots{}

\subsection*{11/3/2805 04:01:31 Various Cameras, C.R.I.S.P.R.: -7th floor}
\label{sec:orgd14b553}

Watson strolled out of the elevator, as though unfazed by the 20 ft tall steel doors (that's about 6 m for Non-Imperials) which whooshed open as he walked through, before closing and repressurizing the chamber. He was even more unfazed by the second pair of 20 ft tall steel doors (I'm not translating the measurement again, you lemmings.) which he walked through, which again whooshed open, and and then whispered shut behind him.

\emph{Ping}

\emph{I see you've arrived Dr. Watson.}

"Yes, I managed to find my way." Watson said, not asking about the mechanofluid tentacle monster which he'd seen reach for him, before slinking back like a dog whacked on the nose with a newspaper, or the massive airlock doors which led only into a hallway exactly like the one one which led up to them, or the person he was communicating with, who he had never seen and who had spoken to him only in thought, depositing half a million credits into his account before offering him a way to make much much more. It did not do well to betray unease.

The voice in his head chose to remain quiet as he continued to walk along the hallway, preceded by his echoes and proceeding with all his wits, he examined what little there was to examine and allowed his mind to speculate on what was to come. The stainless steel walls were joined contiguously with floors and ceilings of the same material. The hall was uniform as far as his eyes could see, like a syringe needle which he had the misfortune to be on the inside of, which was slowly pushing him into some unknown beheomoth.

Amidst the clip clop of his own gait a subtle moaning could be heard. It lent itself to the steady cadence like the precursor to a Lovecraftian melody to which Watson was only the rhythm section, and for which his progress provided the impetus. As the moaning released more of itself Watson himself began to take notice, with only the slightest perking of the ears and not at all abating his stride. It did not do well to betray unease.

The moaning became a scream, taking up the entirety of the Watson's mind, filling up the entire hallway with itself, taking the very air for its own misery, so that you could not help but breathe in helplessness. Watson stopped, and for a moment felt despair.

There. In the hallway was a door. A singular door in the uniform infinity which the hallway showed both before and behind, existed. Watson walked over. His hand, as slow as the approach of death upon a deserving man, went to the touchpad, to open the door, and embrace the despair. The Scream reached a peak, and Watson felt himself bound to open the door. 

His hand stopped. Fear bound it to stop. The Scream stopped.

Watson turned from the door and walked on.

The hallway led to an atrium full of men like Dr. Watson, with hard eyes, hard soles and hardened minds all milling about in the bright white room. On a platform at the far end of the room stood Florence Stronza. As Watson strode in, Florence Stronza began.

"I see everyone is now here. Thank you for coming. For those of you who don't know me, you aren't supposed to." The woman, stood still. "You are here because you have been chosen for a project which is strictly confidential."

The woman stood still, as though waiting for anunciation. Silence took the room for her own, pregnant with gnosis. A wall moved out of view and behind it was a woman, twelve feet tall with marble skin, her breasts bared to the world. All eyes were upon her, waiting for her to open her eyes, her features unmarred by feeling, feeling her visage that of a goddess.

"Meet Mnemosyne."

\subsection*{12/13/2805 23:59:50 Camera 388499500684, Located in the home of Cyril and Gina Ferguson}
\label{sec:org9c4a45a}

Cyril was planning a revolution. Well, sort of. He didn't actually know it yet. But nevertheless he was a revolutionary in the eyes of the woman who arrived on his door step.

\textbf{Knock Knock}

.

.

.

\textbf{Knock Knock Knock}

The door opened revealing Cyril's face, a chubby face with the hint of stubble as though he'd spent most of the night and a better part of the day working madly on some arcane relic of the past, which he had. 

"Oh thank goodness you're still here!" The woman exclaimed, throwing her arms around Cyril and pressing herself against him. Cyril simply looked at the woman, who had pressed her face into his chest.

"Yes, of course I am. And who might you be?"

She looked up at him deeply in his eyes, like violet stained glass revealing the sacred light, and said "Cocknobber88 from the Wallervill3.3dited room."

"Oh yes, well uh, come in." He put his hand on her back and guided her into the room.

Gina looked on with the sweetness of diet cola, and inquired:

"Honey, who is this?"

Cyril looked back at the woman and said:

"Cocknobber88 from RealSpace" The woman looked at the floor as her face flooded with red embarrassment.

"My real name is Amanda." said Cocknobber88. The woman, only slightly smaller than Cyril, walked over and shook Gina's hand.

"Oh, well nice to meet you, I suppose. I'm Gina."

Cyril, not understanding the feelings of the two women, continued "Well, sit down. Would you like something to drink? I got some rather interesting coffee in the other day." 

Amanda nodded at him and sat down on the loveseat. Gina looked at Amanda, looked at Cyril walking away, looked at the loveseat, and sat down next to Amanda.

"So what brings you to our home?" Gina ventured.

"It's private. It's better that you don't get mixed up in it."

"Well, Cyril is my husband. So I should say if it has to do with him, it has to do with me."

"Gina, it's better that you don't know."

Gina glanced at Amanda's waist, and back at her own, and flushed red.

"Well okay miss Cocknobber88."

Amanda brightened red as well.

Returning with a tray with three cups of espresso, Cyril went on quite cheerily, "It's a special hydroponically grown variety, none of the manufactured or synthesized stuff. Evidently it comes from a strain in Old Africa. I hear there's very little of the Plague there and most of the fauna is intact. You see, it's very interesting\ldots{}" So he went and the ladies listened on, eventually he reached a point, when Gina was looking quite bored and Amanda was rubbing her shoes against the carpet at an increasingly rapid rate where he thought to inquire:

"So what did you wish to speak to me about?"

Amanda looked down at her hands before looking up to see Cyril's inquisitive gaze, which lay somewhere in between that of a photogenic puppy, and a madman building an empire.

"Yes, what did you wish to speak with us about?" Gina said, grinning like a skull held aloft in a Shakespeare play.

Amanda looked at Gina, then Cyril. "Are you sure you\ldots{}"

"Yes?" Cyril answered, expecting more information, but accidentally giving a reply. Amanda simply nodded at him.

"You're the one Mac told me about, right?" Amanda glanced at the robot. She had been expecting JC Denton\footnote{The superspy progtagonist of \emph{Deus Ex} a 21st Century cultural artifact which depicted a dystopian modern world full of nano machines. Considered subversive.} and had gotten Doc Brown\footnote{The genius inventor depicted in \emph{Back to the Future}, another 21st Century artifact, which depicted time travel via automobile and featured an incestuous relationship betweeen mother and son. Dissidents such as the Historians were heavily inspired by art from the 21st Century as well as from the Greco-Roman, Renaissance, and Enlightenment periods. They seemed to believe these cultural depictions were in some way more pure or aesthetically pleasing than modern art.}.

"You know Mac?"

Amanda nodded. A board blinked happily in the background.

"Are you ready to go?"

Binary: Go with her.

"Go where?"

Binary: Away.

"Outside the dome. We have to go."

"Why."

Binary: Because it'll be fun!

"Because it's dangerous for people like us to stay here."

"People like us?"

Amanda looked about, and lowered her voice to less than the whisper of time sending ash across the ground of Alexandria, where no library stood. "Historians."

"Well I don't see what's so dangerous about being a historian. I'm a Professor of Archaic Computing Studies and the History of Mathematics. Getting burned by soldering irons and cut by paper books isn't nearly as dangerous as people might think."

She looked at him with shock and frustration.

"Getting electrocuted stings a bit though. You have to watch out for that." Cyril continued, offering sage wisdom to one unaware of his profession.

"No!!" Amanda explained jumping up from the loveseat, spilling coffee on the floor and on her propitiously placed raincoat.

Binary: Just go with it. I'll explain later.

"Oh! That sort of Historian! Well, let me just collect my things! How long are we going for?"

Cyril rushed into his study before he could see Amanda's look of utter inconsternation, which he likely would neither have comprehended nor appreciated to begin with.

\subsection*{12/14/2805 01:33:04 Various Cameras, In the internal externality that is the dome, but not indoors.}
\label{sec:orgd392d89}

The two walked beneath the starless night which was illuminated by the streetlamps the Gaussian historian, and the Historian dissenter. Cyril walked along merrilly, flying along tangents of the days happenings, things that might have been, or were not or may be, in the social sphere that is to say. The days interactions began to lose just the slightest bit of their opaqueness under his prying eye. It occurred to him that he likely should have brought his wife along. She was acting rather strangely after having met Amanda. Surely she was not jealous! Nonetheless, she would likely be rather angry with him when he came back.
\section*{We're off to meet the wizard!}
\label{sec:orgab7741a}
\subsection*{12/14/2805 12:00:01 Dashcam 394182039485, Unknown}
\label{sec:org0ac59de}
It had been silent for the past hour.

The two gazed in wonderment at the world, the still world in which they were the only things alive, the lake of nothingness in which they had dived in. The sky above them was inky lack illuminated by twelve-thousand twelve-thousands of stars, each a saint giving them but a little light, a little guidance, for they were in Heaven's void. Though they did not know the words, they were on the dark side of the moon. Below them was the ground which could not rightly be called earth, the craters and rocks made smooth by their speed, as though they floated along a white marble.

"What are those?" said Amanda, pointing to the stars.

"I don't know." began Cyril. "They don't look like streetlamps."

The two continued, looking at that darkest stretch of space for man's own eyes, seeing only light where none should be, as without so within.

\subsection*{11/13/2805 23:19:42 The Office of Dr. Steven Watson}
\label{sec:orge0269a8}

Watson had a crick in his neck. He'd been pacing back and forth in his office like an autist on LSD, unable to get the woman out of his mind. The woman and the scream. He pulled out a pen and paper and began to write all that he knew about C.R.I.S.P.R., Stronza, and See Corp. Their history, their employers, everyone he'd met.

It came out to scarcely three-quarters of a page of his bullet pointed jackhammer scrawl. 

Watson stared at the page, willing there to be more than there was before sighing. A sip of brandy later and he began searching on the networks. The history of See Corp. and C.R.I.S.P.R. and Stronza, for all of them there was nothing, except what he had written. All his prior knowledge was all there was, which could not possibly be.
\subsection*{Record room}
\label{sec:orgb46a609}
Deep in the heart of C.R.I.S.P.R. an algorithm for anomaly detection let loose a single ping, informing those that cared to listen, that someone was being strange.
\subsection*{Stronza's office}
\label{sec:org4ef89a0}
Stronza received a ping. A single sentence from a slighted strumpet. \textbf{He won't see me.}
\subsection*{The Ministry of Peace}
\label{sec:org98ea0d5}
"I can't believe nobody saw them!" a man ran a hand through his half-hair, leaving a glistening pallete visible, like a bathroom mirror for the light to play off of. A man with a grocery bag for a belly sat down, trying not to overflow his shirt, and waited for explanations.

"Well, nobody ever leaves." A man with the frame of a game of hangman, said, searching for words.

"Are you saying that nobody was watching the gates because nobody goes through them?" exclaimed the bag-man, thinking that he'd lose his shirt. \textbf{Incompetant subordinates.}

The hangman began to sweat. "Well, sir. There were electronic locks, and cameras, and algorithms--"

"They just walked right through!"

"Well, yes sir. And a-and please don't fire me," the hangman gobbled out with his fingers dug into his collar.

The bag-man rolled his eyes, at the spineless miser in front of him. \textbf{How does this happen? How can someone just run off in one of our quadthrusters, right through the gates, without anybody noticing?! Where could they even be going? There's nothing out there!}
\subsection*{A bedroom on the periphery of the city within the dome}
\label{sec:orgbe7ea1c}
Molly lay on her bed, her hair splayed out like a fan, the tail of a peacock missing half it's feathers. Waiting for a ping that would not come, like a woman of a different era, waiting for a man that would not call.

Her eyes were threadbare, as though she could not hear the light through the sheer veil of her mind, seperating her from life, the symbol of immolation on the pyre of a lover. She recalled her second self sealed deep in the heart of C.R.I.S.P.R. The Scream. Her other half was locked away, with no release but the expression of passers by, with none to open the door, none who could hear.

He who has an ear, let him hear.
\end{document}
